---
title: "esm206_lab7"
author: "Eli Schulman"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs

use GGally::ggpairs() to create a pairs plot

```{r}
ggpairs(penguins)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

## Multiple Linear Regression - Penguins

use mult. linear regression to understand relationship between multiple predictor variables and a single outcome var. (body mass)

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

penguin_lm
```

Interpreting penguins_lm coefficient for flipper_length_mm --> expect on average a 51.54 g increase in body mass for every 1 mm increase in flipper length.

### use 'broom' tidy and glance
- broom::tidy to get the coefficient summary
- broom::glance to get the model summary in df

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

in line code to refer to bill depth coefficient --> `r penguin_lm_tidy$statistic[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)
penguin_lm_glance
```

## Try another model

Body mass dependendent on
- flipper length
- species
- sex

```{r}
penguin_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_2
```

## Use plot() to look at model diagnostics

```{r}
plot(penguin_lm_2)
```

--> penguin species, sex and flipper length are reasonable predictor variables. 
--> Diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers


## Make output tables

### 1. Using Model Summary
```{r}
modelsummary(penguin_lm_2)
```

### 2. Using Stargazer
```{r, results = "asis"}
stargazer(penguin_lm_2, type = "html")
```




